% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\pagestyle{empty}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

3385 Michelson Dr\\
Irvine, CA 92612\\
\href{tel:+19492980911}{(949) 298-0911}\\
\href{mailto:jakebodea@gmail.com}{\nolinkurl{jakebodea@gmail.com}},
\href{http://jakebodea.com}{jakebodea.com}

March 24, 2026

Anduril Industries\\
1400 Anduril\\
Costa Mesa, CA 92626

\vspace{\baselineskip}

Dear Anduril Hiring Team:

I am a product-oriented software engineer with a strong background in AI
and mathematics, writing to express my interest in the Senior AI
Engineer position at Anduril. I currently build and ship LLM-powered
agentic systems at TaxRise, a fintech startup based --- fittingly - out
of Anduril's old Irvine office. My experience taking AI products from
prototype to production, combined with my post-grad studies at Stanford,
make this role a natural fit.

Having been an Orange County resident my entire life, I have long
admired Anduril and Palmer Luckey; I've been following his work since
Oculus' acquisition by Meta. I firmly believe Anduril is one of the most
important companies in history. It's where the efficiency and
``impossible'' dreams of the startup-style technology industry face off
against the established military companies to build technology like real
software: shipped fast, iterated in the field, and wired together into
one living system that changes how wars are fought, instead of just
updating the paint job on the last generation's hardware.

I have long wanted to join Anduril, but hadn't found a position that
aligned with my skillset --- until now. I sped through high school and
college, finishing my B.A. in math with triple minors and a 3.96 GPA at
20 years old, right as ChatGPT was released. During my time at Beckman
Coulter, where I started as a senior-year intern and moved to full-time,
my manager told me to go full-steam ahead on this ``AI thing'' and see
how it could benefit the company. After delivering a company-wide
chatbot (full-stack) for our 12,000 employees, I was moved to lead the
internal AI team. Notable projects include a BERT-based ticket
classification system as a tool for the chatbot (before tool use was
common in the industry), RAG-based QA over company documentation, and
computer vision algorithms to automate quality control for our
manufacturing department.

I am now at TaxRise, where our small team of four developers handles all
software development for the company. I solely rebuilt and redesigned
our entire technology suite as full-stack Next.js TypeScript
applications, with repositories optimized for AI coding agents. Once the
apps were mature, I built out a bug triage system turning Slack reports
into Linear issues with PostHog recordings attached, then handing them
off to a coding agent (Cursor, Claude Code, Codex), and finally
producing a well-tested GitHub pull request with video recording for
manual review --- end-to-end autonomous coding infrastructure, from bug
discovery to deployable code. I also led an initiative to add
LLM-powered virtual assistants to each client-facing application, backed
by an MCP server that connects them to our business processes and lets
them take real actions on behalf of clients. These initiatives allowed
our development team to stay nimble and move extremely quickly.

Part of my role is staying current with developments in the AI space and
evangelizing what I find --- turning new ideas into experiments, then
into products and lessons for the team. This is my favorite part of the
job, and I understand it's central to this role as well. The opportunity
to bring this energy to Anduril, where the systems matter and the pace
matches how I naturally work, is what makes this position singular. My
side projects and writing, visible on my website, reflect the same
drive.

I would be delighted to interview and discuss my candidacy in more
detail. Thank you for your time and consideration.

\vspace{\baselineskip}

Sincerely,\\
Jake Bodea

\end{document}
