\documentclass[letterpaper,11pt]{article}

\usepackage{amsmath}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2}\\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingWithDesc}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2}\\
      \text{#3} & \text{#4}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
    \item
     \vspace{-4pt}\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} | \textit{#2} & \textbf{#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.12in, rightmargin=0in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Jake Bodea} \\ \vspace{1pt}
    Irvine, CA $\cdot$ \href{mailto:jakebodea@gmail.com}{\underline{jakebodea@gmail.com}} $\cdot$ \href{tel:9492980911}{\underline{949-298-0911}} $\cdot$ \href{https://www.jakebodea.com}{\underline{jakebodea.com}} $\cdot$
    \href{https://www.linkedin.com/in/jakebodea}{\underline{LinkedIn}} $\cdot$
    \href{https://github.com/jakebodea}{\underline{GitHub}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheadingWithDesc
    {Stanford University}{Stanford, CA}
    {Graduate Certificate in Artificial Intelligence}{2026}
  \item
  \textit{Coursework: Artificial Intelligence: Principles and Techniques, Machine Learning, Natural Language Processing with Deep Learning, Machine Learning from Human Preferences. GPA 4.0}
  \resumeSubheadingWithDesc
    {Concordia University Irvine}{Irvine, CA}
    {Bachelor of Arts in Mathematics | Minors in Computer Science, Business Data Analytics, and Music}{2022}
  \item
  \textit{Summa Cum Laude, Outstanding Mathematics Graduate Award. GPA 3.94}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {TaxRise}{November 2024 - Present}
    {Technical Staff}{Irvine, CA}
    \resumeItemListStart
        \resumeItem{Built ElevenLabs + Twilio + Talkdesk voice and text agents with a custom MCP tool server that executes core client-care actions; currently handling 500+ calls/day with about 80\% resolved without human transfer.}
        \resumeItem{Built a call-intelligence backend processing 5,000+ calls/day into transcripts, summaries, compliance checks, and coaching signals, eliminating about 10 hours/week of manual call review per call-facing employee.}
        \resumeItem{Built AI coaching workflows for 20+ sales reps that simulate failed calls from transcript-derived objections, replacing manual review loops and saving about 1 hour/day per rep.}
        \resumeItem{Owned the full client-platform rebuild by replacing a 60-page Salesforce Experience Cloud portal (Aura/LWC) with custom React/Next.js monorepo applications and leading architecture, implementation, and production cutover.}
        \resumeItem{Established a unified design system and interaction model across intake, status, payment, and document workflows, reducing median time to exit key onboarding statuses from 23 hours to 40 minutes.}
        \resumeItem{Built payment workflows (card, ACH, Plaid, schedule/change/cancel actions) and clearer status UX, shifting operations from rep-managed handling to self-serve and agent-assisted paths.}
        \resumeItem{Built OCR + LLM document pre-screening that auto-matches about 90\% of uploads in 7-10 seconds client-side and reduced manual review staffing from about 40 full-time reviewers to 2 part-time reviewers.}
        \resumeItem{Implemented PostHog feature flags, staged rollouts, and AB-tested kill switches; engineered shared Salesforce auth/session reliability (Redis pooling, distributed locks, retries), reducing org logins from about 6,000/day to about 300/day and eliminating auth-limit outages.}
    \resumeItemListEnd
  \resumeSubheading
    {Stanford University}{October 2024 - Present}
    {Course Facilitator}{Remote}
    \resumeItemListStart
        \resumeItem{Teach, mentor, and grade assignments in XCS229 (Machine Learning) and XCS221 (Principles of AI), guiding students through model formulation, optimization tradeoffs, and implementation debugging.}
    \resumeItemListEnd
  \resumeSubheading
    {Beckman Coulter Diagnostics}{January 2023 - August 2024}
    {Data Scientist}{Brea, CA}
    \resumeItemListStart
        \resumeItem{Led AI Operations delivery as Scrum Master, driving cross-functional execution of internal AI systems from problem framing through deployment and production monitoring across multiple business units.}
        \resumeItem{Built a BERT-based ticket triage API and integrated it into an internal LLM assistant, reducing traditional IT ticket creation by 20\%+ and accelerating mean time to first response for common issues.}
        \resumeItem{Implemented enterprise RAG infrastructure (embedding, vectorization, retrieval, translation) to improve answer quality for the IT assistant, reduce escalation rates for common queries, and cut resolution time.}
        \resumeItem{Developed computer vision inspection models with Manufacturing for automated quality-control and compliance workflows.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading{Super Simple Secret Santa}{TypeScript, TanStack Start}{November 2025}
  \resumeItemListStart
    \resumeItem{Designed and implemented the assignment engine (constraint validation + deterministic pairing rules) to guarantee valid Secret Santa outcomes with exclusion constraints.}
    \resumeItem{Shipped the product end-to-end at \href{https://supersimplesecretsanta.com}{\underline{supersimplesecretsanta.com}} (open-source on \href{https://github.com/jakebodea/secret-santa}{\underline{GitHub}}), reaching about 100 users.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skillset}
\scriptsize{
\textbf{AI/ML \& LLM:} OpenAI, Anthropic Claude, Claude Code, Gemini, Codex, Cursor, BERT, RAG, OCR, AI agents, MCP tooling, embeddings, vector search; \textbf{Languages:} TypeScript, Python, SQL; \textbf{Frontend:} React, Next.js; \textbf{Backend \& APIs:} Node.js, NestJS, REST APIs, GraphQL; \textbf{Cloud/DevOps:} AWS, Cloudflare, Railway, Fly.io, Docker, Kubernetes, GitHub Actions, S3, Lambda, ECS, IAM, RDS, CloudWatch; \textbf{Data:} PostgreSQL, NeonDB, Redis, Databricks; \textbf{Platforms:} Salesforce (Aura, LWC), Stripe, Plaid, Twilio, ElevenLabs, PostHog, Git, Vercel, Bun, Linux
}

\end{document}
